Mortality Trends Among Shelter Residents in Toronto from 2007 to 2024

### 2024-09-27 starter_folder-main/paper/paper.qmd
Small change on code and references.

```{r}
#| include: false
#| warning: false
#| message: false
library(knitr)
library(kableExtra)
library(tidyverse)
```

@@

The data was extracted, cleaned and visualize using R programming language and the whole coding process is done with R (@citeR). Some packages are used throughout the paper, including tidyverse (@cite_tidyverse), ggplot2 (@cite_ggplot), janitor (@citejanitor), OpenDataToronto
(@opendatatorotno), knitr (@cite_knitr), and KableExtra (@cite_kableExtra). Besides, the stater folder from Rohan (@rohan)is used.

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
library(knitr)
library(kableExtra)
library(tidyverse)
library(styler)
style_file("paper/paper.qmd")
```

@@

The data was extracted, cleaned and visualize using R programming language and the whole coding process is done with R (@citeR). Some packages are used throughout the paper, including tidyverse (@cite_tidyverse), ggplot2 (@cite_ggplot), styler (@cite_styler), janitor (@citejanitor), OpenDataToronto
(@opendatatorotno), knitr (@cite_knitr), and KableExtra (@cite_kableExtra). Besides, the stater folder from Rohan (@rohan)is used.
